Sampling requirements to detect ecosystem change

### 2020-03-31 R/manuscript_draft.Rmd

```{r echo=FALSE, eval=F,message=FALSE, warning=FALSE, fig.width = 7.2, fig.height= 3,fig.cap='Distance to real changepoint in biomass per total number of samples analyzed, following (a) random sampling, (b) regular sampling, and (c) iterative sampling. Total number of samples was set between 5 and 30, out of the 74 initial time series.  \\label{fig:case_study_number_sample}'}
#investigating species average biomass
vr_count <- rowSums(vr[,-1])
myoutput_count <- NULL
for (i in 5:30) {
  vrsub <- sample_regular(vr_count, i, input_vector = T, messages = F)
  myoutput_count <- c(myoutput_count, vrsub$method, vrsub$final_n, vrsub$changepoint_all$order.found[j], length(vrsub$changepoint_all$estimates)-2)
  vrsub <- sample_random(vr_count, i, input_vector = T, messages = F)
  myoutput_count <- c(myoutput_count, vrsub$method, vrsub$final_n, vrsub$changepoint_all$order.found[j], length(vrsub$changepoint_all$estimates)-2)
  vrsub <- sample_iterative(vr_count, i, input_vector = T, messages = F)
  myoutput_count <- c(myoutput_count, vrsub$method, vrsub$final_n, vrsub$changepoint_all$order.found[j], length(vrsub$changepoint_all$estimates)-2)
  vrsub <- sample_iterative(vr_count, i, input_vector = T, messages = F, n2 = 6)
  myoutput_count <- c(myoutput_count, vrsub$method, vrsub$final_n, vrsub$changepoint_all$order.found[j], length(vrsub$changepoint_all$estimates)-2)
  vrsub <- sample_iterative(vr_count, i, input_vector = T, messages = F, n2 = 7)
  myoutput_count <- c(myoutput_count, vrsub$method, vrsub$final_n, vrsub$changepoint_all$order.found[j], length(vrsub$changepoint_all$estimates)-2)
}

>>>>

```{r echo=FALSE, eval=F,message=FALSE, warning=FALSE, fig.width = 7.2, fig.height= 3,fig.cap='Distance to real changepoint in biomass per total number of samples analyzed, following (a) random sampling, (b) regular sampling, and (c) iterative sampling. Total number of samples was set between 5 and 30, out of the 74 initial time series.  \\label{fig:case_study_number_sample}'}
#investigating species average biomass
vr_count <- rowSums(vr[,-1])
myoutput_count <- NULL
j=3
for (i in 5:30) {
  vrsub <- sample_regular(vr_count, i, input_vector = T, messages = F)
  myoutput_count <- c(myoutput_count, vrsub$method, vrsub$final_n, vrsub$changepoint_all$order.found[j], length(vrsub$changepoint_all$estimates)-2)
  vrsub <- sample_random(vr_count, i, input_vector = T, messages = F)
  myoutput_count <- c(myoutput_count, vrsub$method, vrsub$final_n, vrsub$changepoint_all$order.found[j], length(vrsub$changepoint_all$estimates)-2)
  vrsub <- sample_iterative(vr_count, i, input_vector = T, messages = F)
  myoutput_count <- c(myoutput_count, vrsub$method, vrsub$final_n, vrsub$changepoint_all$order.found[j], length(vrsub$changepoint_all$estimates)-2)
  vrsub <- sample_iterative(vr_count, i, input_vector = T, messages = F, n2 = 6)
  myoutput_count <- c(myoutput_count, vrsub$method, vrsub$final_n, vrsub$changepoint_all$order.found[j], length(vrsub$changepoint_all$estimates)-2)
  vrsub <- sample_iterative(vr_count, i, input_vector = T, messages = F, n2 = 7)
  myoutput_count <- c(myoutput_count, vrsub$method, vrsub$final_n, vrsub$changepoint_all$order.found[j], length(vrsub$changepoint_all$estimates)-2)
}
